Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-02-21 MS_revised.tex
supp captions
revised captions

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf\newline{Article Title - Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates}
}
\newline
% Insert Author names, affiliations and corresponding author email.
\\
Carlos Pe\~na\textsuperscript{1,*},
Marianne Espeland\textsuperscript{2,3}
\\
\bf{1} Laboratory of Genetics, Department of Biology, University of Turku, Turku, Finland
\\
\bf{2} Museum of Comparative Zoology and Department of Organismic and Evolutionary Biology, Harvard University, Cambridge, USA
\\

@@

% Current address notes
\bf{3} Current address: McGuire Center for Lepidoptera and Biodiversity,
Florida Museum of Natural History, University of Florida, Gainesville,
FL, US.
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

@@

\subsection*{S1 Figure}
\label{S1_Figure}
{\bf Boxplot of speciation (\(\lambda\)) and extinction
(\(\mu\)) values for the 95\% credibility intervals of values estimated
by BiSSE analysis of diversification due to feeding on Solanaceae
plants.}

\subsection*{S2 Figure}
\label{S2_Figure}
{\bf BiSSE analysis of diversification of nymphalids
due to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders}. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders \(\lambda1\), r1).

\subsection*{S3 Figure}
\label{S3_Figure}
{\bf Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution}.

\subsection*{S4 Figure}
\label{S4_Figure}
{\bf Boxplot of speciation and extinction values for
the 95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.}

\subsection*{S5 Figure}
\label{S5_Figure}
{\bf BiSSE analysis of diversification of nymphalids
due to feeding on Apocynaceae hostplants}. Speciation and net
diversification rates are similar.

@@

\subsection*{S17 Figure}
\label{S17_Figure}
{\bf Probability of nodes with
estimated rates from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution}.

\subsection*{S18 supporting information}
\label{S18_Supporting_Information}
{\bf R script for running the BiSSE analysis}.

@@

\subsection*{S23 Figure}
\label{S23_Figure}
{\bf Summary of the MultiMEDUSA
analysis on the 1000 trees from the posterior distribution}.

@@

\subsection*{S25 Figure}
\label{S25_Figure}
{\bf Figure for MEDUSA run on MCC tree from random 1000 trees}.

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf\newline{Article Title - Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates}
}
\newline
% Insert Author names, affiliations and corresponding author email.
\\
Carlos Pe\~na\textsuperscript{1,*},
Marianne Espeland\textsuperscript{2,3,4}
\\
\bf{1} Laboratory of Genetics, Department of Biology, University of Turku, Turku, Finland
\\
\bf{2} Museum of Comparative Zoology, Harvard University, Cambridge, USA
\bf{3} Department of Organismic and Evolutionary Biology, Harvard University, Cambridge, USA
\\

@@

% Current address notes
\bf{4} Current address: McGuire Center for Lepidoptera and Biodiversity,
Florida Museum of Natural History, University of Florida, Gainesville,
FL, US.
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

@@

\subsection*{S1 Fig.}
\label{S1_Figure}
{\bf Boxplot of speciation (\(\lambda\)) and extinction
(\(\mu\)) values for the 95\% credibility intervals of values estimated
by BiSSE analysis of diversification due to feeding on Solanaceae
plants.}

\subsection*{S2 Fig.}
\label{S2_Figure}
{\bf BiSSE analysis of diversification of nymphalids
due to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders}. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders \(\lambda1\), r1).

\subsection*{S3 Fig.}
\label{S3_Figure}
{\bf Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution}.

\subsection*{S4 Fig.}
\label{S4_Figure}
{\bf Boxplot of speciation and extinction values for
the 95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.}

\subsection*{S5 Fig.}
\label{S5_Figure}
{\bf BiSSE analysis of diversification of nymphalids
due to feeding on Apocynaceae hostplants}. Speciation and net
diversification rates are similar.

@@

\subsection*{S17 Fig.}
\label{S17_Figure}
{\bf Probability of nodes with
estimated rates from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution}.

\subsection*{S18 Supporting Information}
\label{S18_Supporting_Information}
{\bf R script for running the BiSSE analysis}.

@@

\subsection*{S23 Fig.}
\label{S23_Figure}
{\bf Summary of the MultiMEDUSA
analysis on the 1000 trees from the posterior distribution}.

@@

\subsection*{S25 Fig.}
\label{S25_Figure}
{\bf Figure for MEDUSA run on MCC tree from random 1000 trees}.
